Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-19 ICML2019/main.tex
pass

\section{Introduction}
\label{sec_intro}
Data analysis techniques have brought significant improvements in a
variety of applications including applications from the medical,
financial, social, and transportation fields. In order to provide
better services, these applications need large amounts of users data
putting at risk the privacy of individual users contributing their data. 
Differential privacy was proposed a decade ago to address these
situations and it on its way to become a gold standard in data
privacy.

Bayesian inference is a standard statistical tool that is useful to
estimate a posterior distribution when given a prior distribution and
some observed data.

In this work we consider the design space of  parametric Bayesian
inference mechanisms guaranteeing differential privacy. Our work is
motivated by recent developments in the area of probabilistic
programming where several tools have been proposed to perfor
parametric and non-parametric Bayesian inference in an efficient
way. The in
for our work is the recent development of

In particular
we focus on two classical models: the Beta-Binomial and the
Dirichlet-Multinomial models. These are classical models

Our work is conducted under a Bayesian inference scenario, where the posterior distribution is the analysis result we obtained from the data.
Publishing the posterior distribution inferred from a sensitive dataset can
leak information about the individuals in the dataset.
In order to guarantee differential privacy and to protect the
individuals' data we can add noise to the posterior before releasing it.
The amount of the noise that we need to introduced
depends on the privacy parameter $\epsilon$ and the sensitivity of the inference to
small changes in the data set. 
Sensitivity can be computed in many different ways based on which metric space
we consider on the output set of the mechanism. In the literature on private Bayesian
inference (\cite{zhang2016differential,xiao2012bayesian}), it is only measured with
respect to the vector of numbers parametrizing the output distribution using, e.g. the $\ell_1$ norm.
A more natural approach which we explore here, is to measure sensitivity with respect to a metric on the space of inferred probability distributions.
A re-loved question is that of how to measure accuracy. Again,
this can be answered in different ways based on the metric imposed on the output space, and yet again
only in few works in literature (e.g. \cite{zhang2016differential})
distances between probability measures have been used for these purposes.

@@

\noindent \textbf{Main contributions.}
\begin{itemize}
	\item We design a new differentially private Bayesian inference mechanism based on the standard exponential mechanism.
	\item We explored two ways to improve the accuracy: 1) calibrating noise to the sensitivity of a metric over distributions (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots). 2) Using a smooth upper bound on the local sensitivity and scale the noise to this smooth bound rather than global sensitivity, to improve the mechanism accuracy.
  \item A full proof on the newly designed mechanism is $(\epsilon, \delta)-$differential privacy is given in paper.
	\item We implemented the new proposed mechanism and other art-of-state mechanisms, comparing the performance in terms of accuracy and privacy.
\end{itemize}

@@

\subsubsection{Standard Exponential Mechanism with Hellinger Metric}
Our exploration starts from the standard exponential mechanism $\expmech(x,u,\candidateset)$, which samples an element from the candidate set $\candidateset$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$:
\[
\underset{z \thicksim \expmech(x,u,\candidateset) }{\Pr}[z=r] = \frac
{\exp(\frac{\epsilon u(x,r)}{2 GS})}
{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon u(x,r')}{2 GS})},
\]
where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function (i.e. the global sensitivity of the Bayesian inference w.r.t the Hellinger distance), calculated by:
\begin{equation*}
GS = 
\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}}\max_{\{r\in \mathcal{R}\}}
|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
\end{equation*}

@@

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
\begin{lem}
\label{lem_acc_lap}
Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
\todo{Is it correct
$\lapmechPr{\dataobs}{\ldots}$? }
\begin{align*}
&
\Pr\left[
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
\right]
\\
&\qquad = 
\begin{cases}
\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
\end{cases}
\end{align*}
where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
\end{lem}
(Proof is in Appendix III)

%  Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.\\  
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.\\
Instantiating $t$ with specific values ($0,1,2$ for example) and $\epsilon = 1$, we get the following accuracy equations on Laplace mechanism:
%\begin{align*}
%&\lapmechPr{\dataobs}{
%\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0
%} = 0.19673467014,\\
%&\lapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
%\end{aligned}
%  } = 0.11932560927,\\
%&\lapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}
%  \end{aligned}
%} = 0.07237464051.
%\end{align*}
%In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
\begin{align*}
&\lapmechPr{\dataobs}{
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
}\\
& \qquad = \begin{cases}
0.19673467014 & t = 0\\
0.11932560927 & t = 1\\
0.07237464051 & t = 2
\end{cases}.
\end{align*}

@@

Given $t$ with the same specific values ($0,1,2$) and $\epsilon = 1$ as above, we get the following accuracy equations on improved Laplace mechanism:

\begin{align*}
&
\Pr\left[
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), z )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
\right]
\\
&\qquad = 
\begin{cases}
\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
\end{cases}
\end{align*}
%Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$. 
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
%\begin{align*}
%&\ilapmechPr{\dataobs}{
%\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}= 0.31606027941,\\
%&\ilapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
%  \end{aligned}
%} = 0.116272079,\\
%&\ilapmechPr{\dataobs}{
%\begin{aligned}
%& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
%& = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}} 
%    \end{aligned}
%} = 0.04277411.
%\end{align*}
%In all cases above, probability values are fixed even data size changes, only the distance are decreasing.
\begin{align*}
&\ilapmechPr{\dataobs}{
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
}\\
& \qquad = \begin{cases}
0.31606027941 & t = 0\\
0.11627207896 & t = 1\\
0.04277410743 & t = 2
\end{cases}.
\end{align*}

\subsection{Accuracy Bound for $\hexpmech$}
\label{subsec_accuracy_smoo}
\begin{lem}
\label{lem_acc_hexp}
  In Beta-binomial model,
  we have following accuracy bound for this mechanism:
%  \begin{align*}
%  \label{eq_acc}
%  & \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  }\\ 
%  = & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}},
%  \end{align*}
%
%  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$
  \begin{align*}
  \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(t)  } }\\ 
  &  = \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}\\
  & \text{ where } c(t) = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
  \end{align*}
\end{lem}

@@

By solving following equations:
%  \[
  %\frac{1}{\nomalizer{\dataobs}} = 0.19673467\ or\ 0.316060279
\begin{align*}
 &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(0)  } \\
 & = 0.19673467 \text{ or } 0.316060279
\end{align*}
%  \]
%  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the correct answer. 
%  \[
%  \frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
\begin{align*}
  &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(1)  }\\
  &= 0.119325609 \text{ or } 0.116272079
\end{align*}
%  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.
%  \[
%\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
%    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%    \cdot
%    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
%    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}
\begin{align*}
 &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c(2)  }\\
 &=0.072374641 \text{ or }  0.042774107
%\]
\end{align*}
we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with two steps from the correct one... etc.

@@

\subsection{Efficiency Evaluation}
\label{subsec_effi}
%The formula for computing the local sensitivity presented in Sec. \ref{sec_mechs}: %$LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
%\[
%LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
%\]
By the triangle inequality of Hellinger distance,
the local sensitivity  (\ref{eq:local_sensitivity_scoring}) presented in Sec. \ref{sec_mechs} can be simplified to
\[
LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs')).
\]
\todo{
Do we need the experimental on this formula?
It is proved mathematically by case analysis.
For any $r \in \mathcal{R}$, we have
\begin{align*}
&\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
& = 
\begin{cases}
\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive}\\
\hellinger(\bysinfer(\dataobs') - \hellinger(\bysinfer(\dataobs), r)& \text{negative}
\end{cases}\\
& \leq 
\begin{cases}
\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
\hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))+
\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs), r)&
\end{cases}\\
&= \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
\end{align*}
I think it would be a proposition.
}

% This equation is validated by an experimental result shown in Fig. \ref{fig_efficiency}. We calculate the $\max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}}$ value for every candidate $r \in \candidateset$. It is shown that maximum value taken when  $r = \bysinfer(\dataobs)$.

% \begin{figure}[ht]
% \centering
% \includegraphics[width=0.45\textwidth]{efficiency.eps}
% \caption{Experimental Results for Finding the Local Sensitivity Efficiently}
% \label{fig_efficiency}
% \end{figure}

>>>>

\section{Introduction}
\label{sec_intro}
Data analysis techniques have brought significant improvements in a
variety of applications including applications from the medical,
financial, social, and transportation fields. In order to provide
better services, these applications need large amounts of users data
putting at risk the privacy of individual users contributing their data. 
Differential privacy was proposed a decade ago to address these
situations and it is on its way to become the gold standard in data
privacy.

Bayesian inference is a standard statistical tool that is useful to
estimate a posterior distribution when a prior distribution is given
and some data is observed.

In this work we consider the design space of  parametric Bayesian
inference mechanisms guaranteeing differential privacy. Our work is
motivated by recent developments in the area of probabilistic
programming where several tools have been proposed to perform
parametric and non-parametric Bayesian inference in an efficient
way.

We focus on two classical models: the Beta-Binomial and the
Dirichlet-Multinomial models. In the Beta-Binomial model the goal
is to estimate an unknown fraction of a population from a sequence
of Bernoulli trials each of which is either 0 or 1 and from an initial
prior belief, a Beta distribution, on that fraction; the trials are assumed to be independent
given the value of the bias. In the Dirichlet-Multinomial model a Multinomial
distribution is used to describe categorical data with more than
two possible outcomes. Similarly, the aim is to learn the various
unknown proportions of a population from a sequence of trials
each of which having more than two possible outcomes. Again,
a prior belief, a Dirichlet distribution, is used to describe the initial knowledge
about those fractions. The posterior distributions on the proportions will be
respectively a Beta distribution and a Dirichlet distribution.

In our work  the posterior distribution is the analysis result we obtained from the data.
While the prior distributions are considerd public information,  publishing the posterior distribution
inferred from a sensitive dataset can leak information about the individuals in the dataset.
In order to guarantee differential privacy and to protect the
individuals' data we can add noise to the posterior before releasing it.
The amount of the noise that we need to introduce
depends on the privacy parameter $\epsilon$ and the sensitivity of the inference to
small changes in the data set. 
Sensitivity can be computed in many different ways based on which metric space
we consider on the output space of the mechanism. In the literature on private Bayesian
inference (e.g. \cite{zhang2016differential,xiao2012bayesian}), it is usually measured on
the vector of numbers parametrizing the output distribution using, e.g. the $\ell_1$ norm.
A more natural approach which we explore here, is to measure sensitivity with respect to
a metric on the space of inferred probability distributions.
Another question is that of how to measure accuracy. Again,
this can be answered in different ways based on the metric
imposed on the output space, and yet again
only in few works in literature (e.g. \cite{zhang2016differential})
distances between probability measures have been used for these purposes.

@@

\noindent \textbf{Main contributions.}
What follows is a summary of the main contributions of this work.
\begin{itemize}
	\item We design a new differentially private Bayesian inference mechanism based on the standard exponential mechanism.
	\item We explored two ways to improve the accuracy: 1) calibrating noise to the sensitivity of a metric over distributions (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots). 2) Using a smooth upper bound on the local sensitivity and scale the noise to this smooth bound rather than global sensitivity, to improve the mechanism accuracy.
  \item A full proof on the newly designed mechanism is $(\epsilon, \delta)-$differential privacy is given in paper.
	\item We implemented the new proposed mechanism and other art-of-state mechanisms, comparing the performance in terms of accuracy and privacy.
\end{itemize}

@@

\subsubsection{Standard Exponential Mechanism with Hellinger Metric}
Our exploration starts from the standard exponential mechanism $\expmech(x,u,\candidateset)$, which samples an element from the candidate set $\candidateset$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$:
\[
\underset{z \thicksim \expmech(x,u,\candidateset) }{\Pr}[z=r] = \frac
{\exp(\frac{\epsilon u(x,r)}{2 GS})}
{\Sigma_{r' \in \mathcal{R}}\exp(\frac{\epsilon u(x,r')}{2 GS})},
\]
where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function (i.e. the global sensitivity of the Bayesian inference w.r.t the Hellinger distance), calculated by:
\begin{equation*}
GS = 
\max_{\{|\dataobs,\dataobs'| \leq 1;\dataobs,\dataobs'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
\end{equation*}

@@

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
\begin{lem}
\label{lem_acc_lap}
Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
\begin{align*}
&
\Pr\left[
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
\right]
\\
&\qquad = 
\begin{cases}
\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
\end{cases}
\end{align*}
where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
\end{lem}
(Proof is in Appendix III)

%  Instantiating $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.\\
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$.\\  
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.\\
Instantiating $t$ with specific values ($0,1,2$ for example), we get the following accuracy equations on Laplace mechanism:
\begin{align*}
&\lapmechPr{\dataobs}{
\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0
} = 0.19673467014,\\
&\lapmechPr{\dataobs}{
\begin{aligned}
& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
\end{aligned}
  } = 0.11932560927,\\
&\lapmechPr{\dataobs}{
\begin{aligned}
& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
& = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}
  \end{aligned}
} = 0.07237464051.
\end{align*}
In all cases above, probability values are fixed even data size changes, only the distance are decreasing.

@@

Given $t$ with the same specific values ($0,1,2$ as above), we get the following accuracy equations on improved Laplace mechanism:
%Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$. 
%
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
%  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%  \cdot
%  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
\begin{align*}
&\ilapmechPr{\dataobs}{
\textstyle\hellinger(\bysinfer(\dataobs), r_L ) = 0}= 0.31606027941,\\
&\ilapmechPr{\dataobs}{
\begin{aligned}
& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
& = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} 
  \end{aligned}
} = 0.116272079,\\
&\ilapmechPr{\dataobs}{
\begin{aligned}
& \textstyle\hellinger(\bysinfer(\dataobs), r_L )^2 \\
& = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}} 
    \end{aligned}
} = 0.04277411.
\end{align*}
In all cases above, probability values are fixed even data size changes, only the distance are decreasing.

\subsection{Accuracy Bound for $\hexpmech$}
\label{subsec_accuracy_smoo}
\begin{lem}
\label{lem_acc_hexp}
  In Beta-binomial model,
  we have following accuracy bound for this mechanism:
%  \begin{align*}
%  \label{eq_acc}
%  & \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  }\\ 
%  = & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}},
%  \end{align*}
%
%  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$
  \begin{align*}
  \lefteqn{ \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c  } }\\ 
  &  = \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}\\
  & \text{ where } c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t).
  \end{align*}
\end{lem}

@@

By solving following equations:
  \[
  \frac{1}{\nomalizer{\dataobs}} = 0.19673467\ or\ 0.316060279
  \]
  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the correct answer. 
  \[
  \frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
   = 0.119325609\ or\ 0.116272079
  \]
  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.
  \[
\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}
     = 0.072374641\ or\ 0.042774107
\]
we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with two steps from the correct one... etc.

@@

\subsection{Efficiency Evaluation}
\label{subsec_effi}
%The formula for computing the local sensitivity presented in Sec. \ref{sec_mechs}: %$LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$
%\[
%LS(\dataobs)=\max_{\substack{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'},\\ r\in \mathcal{R}}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
%\]
By the triangle inequality of Hellinger distance, the local sensitivity  (\ref{eq:local_sensitivity_scoring}) presented in Sec. \ref{sec_mechs} can be simplified to $\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs'))$.
Specifically, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$:
%\begin{equation*}
%\begin{split}
%LS(\dataobs) 
%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) \\
%  & - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
%  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
%\end{split}
\begin{align*}
LS(\dataobs)
& = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
\left|~
\begin{aligned}
&\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs))\\
&\quad - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))
\end{aligned}
\right|\\
  & = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}}
\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs)).
\end{align*}

%\end{equation*}

This equation is validated by an experimental result shown in Fig. \ref{fig_efficiency}. We calculate the $\max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}}$ value for every candidate $r \in \candidateset$. It is shown that maximum value taken when  $r = \bysinfer(\dataobs)$.

\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{efficiency.eps}
\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
\label{fig_efficiency}
\end{figure}
